Effects of CHILDREN's programs

### 2020-02-26 paper.tex
update

\usepackage{alltt}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}

@@

\tableofcontents
\listoftables

% note below table
% https://stackoverflow.com/questions/44549464/table-spacing-issue-converting-to-pdf-via-latex-with-pandoc/44797387#44797387
\listoffigures

@@

Figure \ref{LineDisp}

@@

Table \ref{mealsTripsSubsidyRegressions}
% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
\section{Outline}
Descriptive statistics\\
dynamics of\\ 
(- number of organizations)\\
(- number of beneficiaries)\\
- selected ordinal outcomes, stacked\\
- real total subsidy\\
- real median subsidy per institution\\
- real median subsidy per beneficiary\\
(- which variables have largest variance; also relevant for variable selection)\\

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 15:43:13 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\usepackage{booktabs}

\begin{table}
\caption{Regression Results: Number of meals}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\toprule
 & OLS & OLS without Outliers & OLS Impute \\
\midrule
(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
\midrule
R$^2$       & 0.43            & 0.13            & 0.45             \\
Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
Num. obs.   & 329             & 250             & 440              \\
RMSE        & 39992.79        & 3629.72         & 39601.41         \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{GrantsRegressionsLunch}
\end{center}
\end{table}

Table \ref{GrantsRegressionsLunch}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.70^{***}$ & $2.62^{***}$ & $3.62^{***}$ \\
                 & $(0.33)$     & $(0.23)$     & $(0.33)$     \\
realTripsSubsidy & $0.00^{*}$   & $0.00^{***}$ & $0.00^{*}$   \\
                 & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
\hline
R$^2$            & 0.05         & 0.09         & 0.05         \\
Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
Num. obs.        & 322          & 257          & 334          \\
RMSE             & 2.96         & 1.70         & 2.93         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{GrantsRegressionsTrips}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{HealthRegressions-LessIll}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{HealthRegressions-DietaryKnowledge}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{HealthRegressions-AppreciateHealthy}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{SelfworthRegressions}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{DayToDaySkillsRegressions}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 3:43:31 PM
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 3:43:33 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Less Ill} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 3:43:33 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Dietary Knowledge} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

\usepackage{alltt}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}

@@

\tableofcontents
\listoftables
\listoffigures

@@

@@

% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
\section{Outline}
Descriptive statistics\\
dynamics of\\ 
(- number of organizations)\\
(- number of beneficiaries)\\
- selected ordinal outcomes, stacked\\
- real total subsidy\\
- real median subsidy per institution\\
- real median subsidy per beneficiary\\
(- which variables have largest variance; also relevant for variable selection)\\

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 14:21:55 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
\hline
R$^2$       & 0.43            & 0.13            & 0.45             \\
Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
Num. obs.   & 329             & 250             & 440              \\
RMSE        & 39992.79        & 3629.72         & 39601.41         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of meals}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.70^{***}$ & $2.62^{***}$ & $3.62^{***}$ \\
                 & $(0.33)$     & $(0.23)$     & $(0.33)$     \\
realTripsSubsidy & $0.00^{*}$   & $0.00^{***}$ & $0.00^{*}$   \\
                 & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
\hline
R$^2$            & 0.05         & 0.09         & 0.05         \\
Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
Num. obs.        & 322          & 257          & 334          \\
RMSE             & 2.96         & 1.70         & 2.93         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{table:coefficients}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{table:coefficients}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{table:coefficients}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 14:22:05
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 14:22:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Less Ill} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 14:22:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Dietary Knowledge} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 14:22:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Appreciate Healthy} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
